Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-10-01 paper.qmd
Updated Figure 9 dens calculation with total number of bins (Didn't chnaged: Need to look)

## Find the minimum MSE when have duplicate a1
error_two_curvy_clust_umap <- error_two_curvy_clust_umap |>
  group_by(a1) |>
  filter(bin1 == min(bin1)) |>
  ungroup() |>
  mutate(prop_dens = b_non_empty/side_length)

>>>>

## Find the minimum MSE when have duplicate a1
error_two_curvy_clust_umap <- error_two_curvy_clust_umap |>
  group_by(a1) |>
  filter(bin1 == min(bin1)) |>
  ungroup() |>
  mutate(prop_dens = b/side_length)
